Suplementary information: Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-02 SupplementaryInformation.tex
Start modifying supplementary information

If you consider that the system only varies on the $z$ axis (as show in Fig.
\ref{Fig1}(a)) , the transfer matrix is $M\left(z_{2},z_{1}\right) $
is a
2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%

Many equivalent formulations have been proposed to obtain $M$. For example, if you
have a complete multilayer system and it periodically replicates to form an artificial photonic crystal, then Bloch's theorem can be used to describe the normal
modes of this crystal. According to Bloch's theorem, the modes of a periodic system
may be written as a superposition of Bloch waves, each of which acquires a
\emph{phase factor} as it propagates from one period to the next. Therefore, each
Bloch wave would obey
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ represents a 1D Bloch's
vector corresponding to a wave that propagates along $z$-direction. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that exactly $\det M=1$
is used, so that the product of eigenvalues ought to be $\Lambda_{+}\Lambda_{-}=1$, and the dispersion relation of the Bloch modes may be obtained in
principle from
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials a and b, with refractive indices $n_{a}$ and $n_{b}$, and their
		thickness $d_{a}$ and $d_{b}$ gradually increases according to the condition
		of $1/4$ of the wavelength at wich $j$-th. period will be sintonized.
		\textbf{E}$_{\protect\alpha }^{\protect\beta }$ and \textbf{H}$_{\protect%
			\alpha }^{\protect\beta }$ are the electric and magnetic fields, and \textbf{%
			k}$_{\protect\alpha }^{\protect\beta }$ is the wavevector, where $\alpha
		=\left\{ i,r,a,b\right\} $ corresponds to the medium where the wave is
		traveling and $\beta =\{-,+\}$ to the direction of propagation of the wave
		along the $\pm z$ axis. (b) The multilayer system can be replaced by a broad
		effective layer within which the electric \textbf{E}$_{\protect\beta }$ and
		magnetic \textbf{H}$_{\protect\beta }$ fields, and a Bloch wave \textbf{K}$_{%
			\protect\beta }$ propagate in the positive direction and another set
		propagate in the opposite direction along the $z$ axis.}
	\label{Fig1}
\end{figure}

Now, considering a finite system made of $P$ periods, with $PD$ thickness
and placed on a substrate. For the extreme case of only $P=1$ period, the
optical properties of this system can be obtained by considering an incoming
wave from the ambient, a wave reflected to the environment, a wave
transmitted to the substrate, and two Bloch waves within the structure, one
moving up and other down, as show in Fig. \ref{Fig1}(b).

>>>>

Consider a system that varies along  the $z$ axis only, as show in Fig.
\ref{Fig1}(a). Its transfer matrix $\bm{M}(z_{2},z_{1})$
is a
2x2 matrix that relates the components  $E_{\parallel }$ and
$H_{\parallel }$ of the electric and magnetic fields parallel to the $xy$ plane and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=\bm M( z_{2},z_{1}) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%

Many equivalent formulations have been proposed to obtain $\bm M$. For
a periodically
replicated multilayered system, the transfer matrix may be constructed
from the normal modes of the corresponding photonic crystal. These
modes are described by Bloch's
theorem, which reads in this case,
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=\bm M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ is the 1D Bloch's
vector describing the propagation along $z$. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $\bm M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that $\det M=1$  exactly,
so the product of eigenvalues $\Lambda_{+}\Lambda_{-}=1$ and the
dispersion relation of the Bloch modes becomes
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,\bm M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
		thickness $d_{a}$ and $d_{b}$ gradually increases according to the condition
		of $1/4$ of the wavelength at wich $j$-th. period will be sintonized.
		\textbf{E}$_{\protect\alpha }^{\protect\beta }$ and \textbf{H}$_{\protect%
			\alpha }^{\protect\beta }$ are the electric and magnetic fields, and \textbf{%
			k}$_{\protect\alpha }^{\protect\beta }$ is the wavevector, where $\alpha
		=\left\{ i,r,a,b\right\} $ corresponds to the medium where the wave is
		traveling and $\beta =\{-,+\}$ to the direction of propagation of the wave
		along the $\pm z$ axis. (b) The multilayer system can be replaced by a broad
		effective layer within which the electric \textbf{E}$_{\protect\beta }$ and
		magnetic \textbf{H}$_{\protect\beta }$ fields, and a Bloch wave \textbf{K}$_{%
			\protect\beta }$ propagate in the positive direction and another set
		propagate in the opposite direction along the $z$ axis.}
	\label{Fig1}
\end{figure}

Now, consider a finite system made of $P$ periods, with thickness $PD$
and placed on a substrate. Even for the extreme $P=1$  case, the
optical properties of this system can be obtained by considering an incoming
wave from the ambient, a wave reflected to the environment, a wave
transmitted to the substrate, and two Bloch waves within the structure, one
moving up and other down, as show in Fig. \ref{Fig1}(b).
